### 2021-12-08 manuscript.tex
Finish first raw draft (perhaps) [ci skip]
This build is based on
https://github.com/lubianat/quali_phd/commit/16dae36f6c7f242d28e67659bf25890260f681f0.

This commit was created by the following CI build and job:
https://github.com/lubianat/quali_phd/commit/16dae36f6c7f242d28e67659bf25890260f681f0/checks
https://github.com/lubianat/quali_phd/actions/runs/1555915703

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/8e4db1e93b09d5722f9c3655e461f238c65e0391/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/8e4db1e93b09d5722f9c3655e461f238c65e0391}{lubianat/quali\_phd@8e4db1e}
on December 8, 2021.

@@

The dashboard includes not only a basic list of read articles, but also statistics on most read authors and most read venues.
It also displays an interactive map of the instituions of articles read, permitting a glance on geographic biases in activities.
An example of queries is show in \ref{fig:dashboard}.
As the queries are rendered live, they evolve in quality with the growth of Wikidata.
Finally, the clean 5-star-open data format enables users to adapt the queries to include different aspects of Wikidata.
For example, table \ref{tbl:articles_read_hca} showcases 10 articles that (1) I have read in the past year and (2) were authored by a speaker of the 1st Human Cell Atlas Latin America Single Cell RNA-seqData Analysis Workshop {[}\protect\hyperlink{ref-1hag8XE6}{133}/{]}.
One practical application that the dashboard enables, thus, is to identify people in an event, institution or location that the user has read before, therefore catalysing the possibility of colaborations.
Anedoctally, this strategy was tested successfully at Biohackathon Europe 2021 {[}\protect\hyperlink{ref-kHL3NVxk}{134}/{]}, where I used the system both to identify possible collaborators and as a conversation starter.
\textbar workLabel \textbar authors \textbar{}
\textbar-------------------------------------------------------------------------------------------------\textbar--------------------------------------------------------------------------\textbar{}
\textbar A promoter-level mammalian expression atlas \textbar Jay W Shin \textbar{}
\textbar Single-cell RNA-seq reveals new types of human blood dendritic cells, monocytes, and progenitors.\textbar Muzlifah Haniffa \textbar{}
\textbar The Human Cell Atlas. \textbar Musa Mhlanga, Jay W Shin, Muzlifah Haniffa, Menna R Clatworthy, Dana Pe'er\textbar{}
\textbar The Human Cell Atlas: Technical approaches and challenges. \textbar Jay W Shin \textbar{}
\textbar Innate Immune Landscape in Early Lung Adenocarcinoma by Paired Single-Cell Analyses. \textbar Dana Pe'er \textbar{}
\textbar Single cell RNA sequencing of human liver reveals distinct intrahepatic macrophage populations \textbar Sonya A MacParland \textbar{}
\textbar Single-cell reconstruction of the early maternal--fetal interface in humans \textbar Muzlifah Haniffa \textbar{}
\textbar Distinct microbial and immune niches of the human colon \textbar Rasa Elmentaite, Menna R Clatworthy \textbar{}
\textbar A cell atlas of human thymic development defines T cell repertoire formation \textbar Muzlifah Haniffa, Menna R Clatworthy \textbar{}
\textbar Decoding human fetal liver haematopoiesis \textbar Muzlifah Haniffa \textbar{}
Table: Articles read by Tiago Lubiana before 8 December 2021 in which an author was a speaker at HCA Latin America
\{\#tbl:articles\_read\_hca\} \textbar{}

>>>>

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/16dae36f6c7f242d28e67659bf25890260f681f0/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/16dae36f6c7f242d28e67659bf25890260f681f0}{lubianat/quali\_phd@16dae36}
on December 8, 2021.

@@

The dashboard includes not only a basic list of read articles, but also statistics on most read authors and most read venues.
It also displays an interactive map of the instituions of articles read, permitting a glance on geographic biases in activities.
An example of queries is show in \ref{fig:dashboard}.
As the queries are rendered live, they evolve in quality with the growth of Wikidata.
Finally, the clean 5-star-open data format enables users to adapt the queries to include different aspects of Wikidata.
For example, table \ref{tbl:articles_read_hca} showcases 10 articles that (1) I have read in the past year and (2) were authored by a speaker of the 1st Human Cell Atlas Latin America Single Cell RNA-seqData Analysis Workshop {[}\protect\hyperlink{ref-1hag8XE6}{133}/{]}.
One practical application that the dashboard enables, thus, is to identify people in an event, institution or location that the user has read before, therefore catalysing the possibility of colaborations.
Anedoctally, this strategy was tested successfully at Biohackathon Europe 2021 {[}\protect\hyperlink{ref-kHL3NVxk}{134}/{]}, where I used the system both to identify possible collaborators and as a conversation starter.

\begin{tablenos:no-prefix-table-caption}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2286}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0974}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.6740}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
workLabel
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
authors\_in\_the\_conference
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
DOI
\end{minipage} \\
\midrule
\endhead
A promoter-level mammalian expression atlas & Jay W Shin & https://doi.org/10.1038/NATURE13182 \\
Single-cell RNA-seq reveals new types of human blood dendritic cells, monocytes, and progenitors. & Muzlifah Haniffa & https://doi.org/10.1126/SCIENCE.AAH4573 \\
The Human Cell Atlas. & Musa Mhlanga, Jay W Shin, Muzlifah Haniffa, Menna R Clatworthy, Dana Pe'er & https://doi.org/10.7554/ELIFE.27041 \\
The Human Cell Atlas: Technical approaches and challenges. & Jay W Shin & https://doi.org/10.1093/BFGP/ELX029 \\
Innate Immune Landscape in Early Lung Adenocarcinoma by Paired Single-Cell Analyses. & Dana Pe'er & https://doi.org/10.1016/J.CELL.2017.04.014 \\
Single cell RNA sequencing of human liver reveals distinct intrahepatic macrophage populations & Sonya A MacParland & https://doi.org/10.1038/S41467-018-06318-7 \\
Single-cell reconstruction of the early maternal--fetal interface in humans & Muzlifah Haniffa & https://doi.org/10.1038/S41586-018-0698-6 \\
Distinct microbial and immune niches of the human colon & Rasa Elmentaite, Menna R Clatworthy & https://doi.org/10.1038/S41590-020-0602-Z \\
A cell atlas of human thymic development defines T cell repertoire formation & Muzlifah Haniffa, Menna R Clatworthy & https://doi.org/10.1126/SCIENCE.AAY3224 \\
Decoding human fetal liver haematopoiesis & Muzlifah Haniffa & https://doi.org/10.1038/S41586-019-1652-Y Table: Articles read by Tiago Lubiana before 8 December 2021 in which an author was a speaker at HCA Latin America \\
\{\#tbl:articles\_read\_hca\} & & \\
\bottomrule
\end{longtable}

\end{tablenos:no-prefix-table-caption}
